---
title: DV_RProject3
author: Brian Yeh, Valentina Chen
output: html_document
---

```{r echo=FALSE, message=FALSE}
setwd("C:/Users/Brian Yeh/Github/DataVisualization/DV_RProject3/00 Doc")
file_path <- "../County_Fairs_in_New_York_State.reformatted.csv"
df_Fairs <- read.csv(file_path, stringsAsFactors = FALSE)

file_path <- "../Path_Through_History_Program_Sites.reformatted.csv"
df_History <- read.csv(file_path, stringsAsFactors = FALSE)

file_path <- "../Wastewater_Treatment_Plants.reformatted.csv"
df_Wastewater <- read.csv(file_path, stringsAsFactors = FALSE)

file_path <- "../New_York_City_Farmers_Markets.reformatted.csv"
df_Farmers <- read.csv(file_path, stringsAsFactors = FALSE)

file_path <- "../New_York_State_Career_Centers.reformatted.csv"
df_Careers <- read.csv(file_path, stringsAsFactors = FALSE)



require("jsonlite")
require("RCurl")
require(extrafont) 
require(tidyr)
require(dplyr)
require(ggplot2)

  
```

###Summary of dataframe  
Join of Career center and county Fairs on Zip code
```{r echo=FALSE}
source("../01 Data/Dataframes_All.R", echo = TRUE)
names(df_Farmers)[names(df_Farmers)=="ZIP_CODE"] <- "ZIP"
names(df_History)[names(df_History)=="ZIP_CODE"] <- "ZIP"

career_center <- dplyr::inner_join(county_fair, career_center, by="ZIP")
summary(career_center)

```
  
###Subset of dataframe joining farmers markets and career centers in New York by Zip code: Where County = Queens
```{r}


```
  
###How many fairs does each region have?
```{r}

new_df <- dplyr::left_join(df_History, df_Fairs, by = "County")
meh <- new_df %>% filter(Fair_Name != "NA") %>% group_by(Region, Fair_Name) %>% summarise(count = n()) %>% arrange(Region, Fair_Name, count) %>% ggplot(., aes(x = Region, y = count, color = Fair_Name, fill = Fair_Name)) + geom_bar(Position = "dodge", stat = "identity")+ theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position = "right") 
meh

```

###Which Zip Codes have Both career centers and county fairs? 
Knit HTML is not showing the Counts with 2 for some reason. I don't know why, but it shows in RStudio
```{r}

career_county <- dplyr::full_join(career_center, county_fair, by="ZIP") %>% group_by(ZIP) %>% summarise(count = n()) %>% ggplot(aes(x = ZIP, y = count)) + geom_point(stat="identity") +
    scale_y_continuous(breaks=c(0,1,2))

career_county


```

###Farmers Markets with Wastewater Facilities in the same Zip Code
```{r}
new_data <- dplyr::full_join(df_Farmers, df_Wastewater, by = "Zip_Code")
new_data %>% filter(Farmers_Market_Name != "NA" & Facility_Name != "NA" & Zip_Code != "NA") %>% group_by(Zip_Code, Farmers_Market_Name, Facility_Name) %>% summarise(count = n()) %>% arrange(Zip_Code, Farmers_Market_Name, Facility_Name, count) %>% ggplot(., aes(x = Farmers_Market_Name, y = count, fill = Facility_Name)) + geom_bar(Position = "dodge", stat = "identity")+ theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position = "right")

```

